%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{enumitem}
\pagestyle{fancy}
\fancyhf{}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Shubham}{Singh}{ 
\href {mailto:shubhamsingh1840@gmail.com}{\faEnvelope \hspace{.05cm} shubhamsingh1840@gmail.com} \hspace{.5cm}
\href {https://www.linkedin.com/in/shubh-singh/}{\faLinkedin \hspace{.05cm} shubh-singh} \hspace{.5cm}
\href {https://github.com/shubhsting}{\faGithub \hspace{.05cm} shubhsting} \hspace{.5cm}
\faPhone \hspace{.05cm} 8076221840/9084810011 
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t][0pt]{0.65\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}



\href{https://www.amazon.com}{\runsubsection{AMAZON}}
\descript{|\hspace{0.1 cm} Software Development Engineer 2}
\location{October 2021 – Present \hspace{0.1 cm} | \hspace{0.1 cm} Bengaluru, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space

% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item working with Business Data Technology(BDT) team to raise the bar of Data Quality Standards on huge Amazon Datasets and create React, Java, Typescript and Python based product from scratch.
\item created, designed and developed internal Data Quality Framework for S3 from scratch that scans s3 buckets, calculates multiple statistics and persists them into DynamoDB based persistence service. The feature have scanned more than 13k+ buckets till date which helped in detecting multiple data quality issues and eventually cleaning up the data lake by deprecating ~2k buckets saving IMR of ~5k dollars per month.
\item collaborated with multiple senior engineers and SDE's in creating a reconciliation platform that ensures same outputs being reflected by multiple computes when a same query is run on them. The S3 readers were again reused in this feature and were building blocks which ran statistics on s3 outputs of these computes and matched them. This eventually led to detection of around 53 issues within 2 weeks of release in around 6 computes. The reconciliation reports generated by this tool soon became VP goal and was monitored and acknowledged by senior management.
\item worked on resuming stats generation request by re-using already calculated stats in cluster in case of retries which led to IMR reduction by 18\%, created and designed DQ UI from scratch which onboarded ~2k live customers into the platform, added pre-validation for requests that reduced huge OE load from ~3k failed requests to 0 and reduced ticket inflow by 40\%. 
\item received multiple accolades from senior engineers for creating wikis which acts as source of information for all new hire on boarding programs, and eventually got promoted to SDE-2 within a span of 1.4 years for exceptional performance. The average SDE-2 promotion timeline is 2 years across BDT.
\end{tightemize}
\sectionsep

\href{https://www.interviewbit.com}{\runsubsection{INTERVIEWBIT}}
\descript{|\hspace{0.1 cm} Software Development Engineer Intern    }
\location{July 2021 – October 2021 \hspace{0.1 cm}|\hspace{0.1 cm} Bengaluru, India}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space

% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Worked on Ruby on Rails and React based traditional interviewbit portal.
\item contributed in writing backend from scratch for IB's stand alone online compilers ,CRUD operations on snippets and features such as fork and share them along with adding features such as run as custom input for failed test cases etc.
\item built key features on problem page such as show previous submissions,retrieve last submitted code to enhance user experience.
\item worked on migrating videos from S3 to youtube that led to overall cost reduction from \$900 to \$100 per month for IB's event pages.
\end{tightemize}
\sectionsep


\href{https://credflow.in}{\runsubsection{Credflow}}
\descript{|\hspace{0.1 cm} Software Development Engineer Intern }
\location{ Jan 2021 – June 2021 \hspace{0.1 cm} | \hspace{0.1 cm} Delhi, India}
\begin{tightemize}
\item contributed in multiple products based on React.js, Node.js, postgres, Git, Redis, Sequelize, Electron and Express.
\item built key features such as share receipts automatically,quotations,show tally Groups from scratch to directly impact more than 5000+ B2B clients.
\item enhanced Desktop Application capabilities by changing its dataflow to use S3 to migrate zipped data to backend which changed its competence and directly helped large clients with huge data sets.
\item restructured the Analytics portal by changing inefficient queries and database schemas which led to the restarting of several key features such as projected collections etc.
\item worked on adding several key features to admin panel along with revamping partner panel from scratch which helped the organization to increase its growth in all aspects.
\end{tightemize}
\sectionsep

% \href{https://www.precisely.co.in/}{\runsubsection{Precisely}}
% \descript{| Software Engineer Intern (Backend) }
% \location{May 2019 – Aug 2019 | New Delhi, India}
% \begin{tightemize}
% \item Worked on Node.js,MongoDB based product
% \item  Worked with the Precisely Backend team,to design and develop the portals of quizes that were conducted by the organization by validating and writing backend along with getting familiar to NodeJS and MongoDB.
% \item coordinated with the Mobile team to write backend for dashboard,internship opportunities and other screens to replicate the web application workflow. 
% \item  Communicate all the finalized back end layout to front end team and render the faulty codes for smooth functioning of application.
% \end{tightemize}
\sectionsep



% \section{Achievements}

% \textbullet{} \textbf {Codechef 4 star (Rating 1857).}\\
% \textbullet{} leading the tech team of an early stage startup  \textbf{Ripen} which have been seed funded by  \textbf{GradCapital} and our beta product is  under progress.\\
% \textbullet{} Secured 190th position among 19000 students
% in July Codechef Long Challenge.\\
% \textbullet{} Secured 3rd position among 4000 participants 24 hr
% hackathon HackVSIT 2020.\\
% \textbullet{} 15+ Youtube video lectures on 
% advance algorithms with viewing 
% time of more than 3000 minutes.

% \sectionsep

\end{minipage}
\hfill
\begin{minipage}[t][0pt]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% \section{Profiles} 
% Codechef:// \href{https://www.codechef.com/users/shubhsting}{\bf shubhsting} \\
% HackerRank://  \href{https://www.hackerrank.com/profile/shubhsting}{\bf shubhsting} 
% \sectionsep


\section{Achievements}

\textbullet{} \textbf {Codechef 4 star (Rating 1857).}\\
% \textbullet{} leading the tech team of an early stage startup  \textbf{Ripen} which have been seed funded by  \textbf{GradCapital} and our beta product is  \\under progress.\\
\textbullet{} Secured 190th position among 19000 \\students
in July Codechef Long Challenge.\\
\textbullet{} Secured 3rd position among 4000 participants 24 hr
hackathon HackVSIT 2020.
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

% \runsubsection{ZOOMOBOARD}
% \href{https://zoomoboard.herokuapp.com/}{\faLink}\hspace{.5cm}
% \href{https://github.com/shubhsting/ZOOMOBOARD}{\faGithub}

% \descript{}
% \location{}
% % \descript{Mar 2012 – May 2013}
% % \location{ | Ithaca, NY}
% \begin{tightemize}
% \item The proposed clone application uses Node.js and supports features like write, erase, redo, undo, upload, download, night mode, current participants ,meeting attendee report,sharing admin Rights etc along with profile viewing options.
% \end{tightemize}
\runsubsection{ripen} \hspace*{\fill}
\href{https://ripen.in}{\faLink}
\descript{}
\location{}

\item Used React,Node to create frontend and wrote backend from scratch to achieve functionalities such as Subscription Management,Usage Report,Send bulk emails and a number of other numerous features for different partner types.


\sectionsep
\runsubsection{ZOOMOBOARD} \hspace*{\fill}
\href{https://zoomoboard.herokuapp.com/}{\faLink} \hspace{0.2cm}
\href{https://github.com/shubhsting/ZOOMOBOARD}{\faGithub}
\descript{}
\location{}
\item The proposed application uses Node.js and supports features like write, erase, redo, undo, upload, download, night mode, current participants , meeting attendee report, sharing admin Rights etc along with profile viewing options.

\sectionsep

\runsubsection{PEXCEL }\hspace*{\fill}
\href{https://github.com/shubhsting/NODE_OSS_PEP/tree/master/Lec5_Excel_Electron}{\faGithub}

\descript{}
\location{}
\item Contemplated a novel approach for achieving the functionalities of Microsoft Excel using Electron framework and JQuery library of Node.js which justifies the application of graph and recursion algorithm working together.
\sectionsep

\section{Skills}
\subsection{Languages}
\textbullet{} Java 
\subsection{Frameworks and Libraries}
\textbullet{} NodeJS  
\textbullet{} React
\subsection{Database}
\textbullet{} MySQL 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% College of Engineering \\
% Magna Cum Laude\\
% \location{ Cum. GPA: 3.83 / 4.0 \\
% Major GPA: 3.9 / 4.0}
% \sectionsep

% \subsection{Golden Heart Academy}


% \section{Certifications}

% Data Structures \\
% HackerRank Problem Solving(Basic and Intermediate)\\
% Object Oriented Programmming \\
% Data Base Management System \\
% Web Development using Node.js
% \sectionsep

\section{Education} 

\subsection{Guru Gobind Singh}
\subsection{Indraprastha University}
\subsection{(GGSIPU),New Delhi}
\descript{BTech in Computer Science}
\location{Aug 2017 - May 2021}
\location{CGPA: 8.6/10}

% \textbullet{} more than 500+ collective submissions\\
% on Leetcode and GeeksForGeeks.


% \sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill



\end{document}  \documentclass[]{article}
